---
title: "R Notebook"
output: html_notebook
---

# Environment setup
```{r}
library(tidyverse)
library(lubridate)
library(janitor)
library(ggpubr)
library(rstatix)
set.seed(9999)
```

# Data load
user id: unique identifier of the user
test: whether the user was exposed to advertising (1) or was in the control group (0)
converted: whether the user converted (1) or not (0)
tot_impr: total number of ad impression the user encountered
mode_impr_day: day of the week user encountered the most number of impression (1) Mon, ..., (7) Sunday
mode_impr_hour: hour of the day in which user encountered the most number of impression (0-23)

```{r}
data <- read.csv("rocketfuel_data.csv")
attach(data)

skimr::skim(data)
```

# Data cleaning & pre-processing
```{r}
# Remove users with null values if any
data <- data %>% 
  drop_na(user_id, test, converted, tot_impr, mode_impr_day, mode_impr_hour)

# Convert into categorical
data$test = as.factor(data$test)
data$converted = as.factor(data$converted)
data$mode_impr_day = as.factor(data$mode_impr_day)
data$mode_impr_hour = as.factor(data$mode_impr_hour)
```

# Q1. Was the experiment randomized properly?
By comparing control and treatment groups
```{r}
# Split control and treatment datasets
data_control <- data[data$test == 0,]
data_treatment <- data[data$test == 1,]

# Check the number of rows
nrow(data_control)
nrow(data_treatment)
```

```{r}
# Scale up the treatment group the same size as the control group
data_treatment_scaled <- sample_n(data_treatment,nrow(data_control))

# Check the number of rows
nrow(data_control)
nrow(data_treatment_scaled)

# Combine the datasets again
data_combined <- rbind(data_control,data_treatment_scaled)
```

```{r}
ggplot(data_combined, aes(tot_impr, fill=test)) + 
   geom_histogram(alpha = 0.5, position = 'identity') + 
   xlim(0,200) +
   labs(title = "Impression distribution in control & treatment groups")
```
```{r}
# Remove outliers that fall outside 3SD from median and have no impression
data_cleaned <- data %>%
  filter(!(abs(tot_impr - median(tot_impr)) > 3*sd(tot_impr))) %>% 
  filter(tot_impr>=1)

# Check the number of rows
nrow(data)
nrow(data_cleaned)

# Also split clean data into control and treatment datasets
data_control_cleaned <- data_cleaned[data_cleaned$test == 0,]
data_treatment_cleaned <- data_cleaned[data_cleaned$test == 1,]
```


# Q1a. Report the share of users allocated to the control group to 6 decimal points
```{r}
# Report the share of row data
control_data =  nrow(data[data$test == 0, ]) / nrow(data)
format(round(control_data, 6), nsmall = 6)  
```

```{r}
# Report the share of row data after removing outliers
control_data_cleaned =  nrow(data_cleaned[data_cleaned$test == 0, ]) / nrow(data_cleaned)
format(round(control_data_cleaned, 6), nsmall = 6)  
```


# Q1b. Conduct an analysis to test if the experiment was properly randomized

## Perform 2-sided z-test if there's significant difference between groups
```{r}
# Perform 2-sided z-test, with raw data
n_control = nrow(data_control)
n_treatment = nrow(data_treatment)

n_control_converted = nrow(data_control[data_control$converted == 1,])
n_treatment_converted = nrow(data_treatment[data_treatment$converted == 1,])

prop.test(x = c(n_control_converted, n_treatment_converted), n = c(n_control, n_treatment), 
          p = NULL, alternative = "two.sided", correct = TRUE)

# p-value = 1.999e-13, which is significant
# we can conclude that the proportion of conversion is significantly different in the two groups
```

```{r}
# Perform 2-sided z-test, with cleaned data
n_control_cleaned = nrow(data_control_cleaned)
n_treatment_cleaned = nrow(data_treatment_cleaned)

n_control_cleaned_converted = nrow(data_control_cleaned[data_control_cleaned$converted == 1,])
n_treatment_cleaned_converted = nrow(data_treatment_cleaned[data_treatment_cleaned$converted == 1,])

prop.test(x = c(n_control_cleaned_converted, n_treatment_cleaned_converted), n = c(n_control_cleaned, n_treatment_cleaned), 
          p = NULL, alternative = "two.sided", correct = TRUE)

# p-value = 5.471e-14, which is significant
# we can conclude that the proportion of conversion is significantly different in the two groups
```

## if test is a predictor of other variables
```{r}
# if test predicts total number of impression, with raw data
logit1 = glm(data = data, test~tot_impr, family = 'binomial')
summary(logit1)
# p-value = 0.831, which is not significant

# if test predicts total number of impression, with cleaned data
logit2 = glm(data = data_cleaned, test~tot_impr, family = 'binomial')
summary(logit2)
# p-value = 0.0507, ~0.05, which is significant
```

```{r}
# if test predicts the day of the week user encounter most impressions, with raw data
logit3 = glm(data = data, test~mode_impr_day, family = 'binomial')
summary(logit3)
# all days of week are significant, except Fridays

# if test predicts the day of the week user encounter most impressions, with cleaned data
logit4 = glm(data = data_cleaned, test~mode_impr_day, family = 'binomial')
summary(logit4)
# all days of week are significant, except Fridays
```

```{r}
# if test predicts the hour of the day user encounter most impressions, with raw data
logit5 = glm(data = data, test~mode_impr_hour, family = 'binomial')
summary(logit5)
# only hour22 and hour23 are significant

# if test predicts the hour of the day user encounter most impressions, with raw data
logit6 = glm(data = data_cleaned, test~mode_impr_hour, family = 'binomial')
summary(logit6)
# only hour22 and hour23 are significant
```


# Q2. Was the campaign effective in increasing conversion rates?

```{r}
# Compute the conversion rate of control users
control_conversion =  nrow(data[data$test == 0 & data$converted == 1, ]) / nrow(data[data$test == 0, ])
control_conversion
#1.78%

# Compute the conversion rate of treatment users
treatment_conversion = nrow(data[data$test == 1 & data$converted == 1, ]) / nrow(data[data$test == 1, ])
treatment_conversion
# 2.55%

# Compute % of consumers converted as a result of the ad campaign
treatment_conversion - control_conversion
# 0.75=7%

# Compute the conversion rate uplift
treatment_conversion / control_conversion
# 1.43 times
```


```{r}
# Run a logistic regression to evaluate impacts on conversion rates

logit7=glm(data = data_cleaned, converted~test+mode_impr_day+mode_impr_hour+tot_impr, family = 'binomial')
summary(logit7)

# test1 estimate=0.4581665, which is positively correlated
# p-value=6.94e-16, which is significant
```

# Export the cleaned dataset in csv
```{r}
write_csv(data_cleaned, "data_cleaned.csv")
```
